---
title: "jones_hw2"
author: "djones47"
date: "2/3/2020"
output: html_document
---
5.
```{r}
v <- c(8:19) #creating vector v, then printing vector v
v

# 5. creating vector w that is a subset of the first 4 elements of v
w <- c(v[1:4])
w

```

6.
```{r}

#creating and printing vector d
d <- c(8:20)
d

#6. creating and printing vector h that is a subset of the middle 5 elements of d
h <- c(d[5:9])
h
```

7.
```{r}
# 7. what is the length of vector w?
length(w)
```

8. The three properties of a vector are the type, the length and the attributes

9. I predict `c(3,False)` will be a double, `c("a,1)` will be a character, and `c(4L,2)` will also be a double

10: The 4 types of common atomic vectors are character, numeric, integer, and logical. The two uncommon types are complex and raw

11. `1=="1"` is true because I think the character must be coerced into an integer or a double? I think `-1<FALSE` is true because false will become a O and -1<0 is true. `One < 2` is false because I don't believe R can convert one to 1 so they cannot be truely compared. 

12. Maybe NA gets changed to a 0 which would be FALSE which is part of a logical vector?

13. Provide the value of the last element in the result of the vector operation `d*2` from the vectors defined above
```{r}
#Creating vector e, then determining the last value in e
e <- d*2
e
e[13]

```

14. Create a vector `a` with a sequence of 11 elements ranging from 0.6 to 1.9 then create a logical vector `b` that identifies which elements in `a` are greater than or equal to 1.1
```{r}
#creating vector a 
a <- seq(from = 0.6, to = 1.9, length = 11)
a

#creating vector b
b <- which(a >= 1.1)
b
```



